Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Typo

But which semantics? We deemed the exchange law of Figure~\ref{fig:naive-impl}
as "clearly wrong" with respect to overloading. There is nothing wrong per se :
we could chose a semantics for intersections that validate this rule.  However,
the resulting system wouldn't capture overloading, and is arguably not very
interesting nor useful. In~\cite{KeilThiemannUnionIntersection}, the authors
argue for basing the semantics of contracts on union and intersection type
systems, which have a simple and natural definition from which the other
properties follow. This approach makes sense, and has been continued in future
works, and in particular in~\cite{RootCauseOfBlame}.

@@

Let us recast the problematic example of Figure~\ref{fig:inter-flat-contracts}
in Figure~\ref{fig:inter-flat-contracts-2}). The execution now splits the
intersection into two sub-contracts that are checked separately. If one
component fails, a flag in a global state. In particular, the two threads don't
interact directly, and don't raise blame by themselves, leading this example run
as expected.

>>>>

But which semantics? We deemed the exchange law of Figure~\ref{fig:naive-impl}
as ``clearly wrong'' with respect to overloading. There is nothing wrong per se :
we could chose a semantics for intersections that validate this rule.  However,
the resulting system wouldn't capture overloading, and is arguably not very
interesting nor useful. In~\cite{KeilThiemannUnionIntersection}, the authors
argue for basing the semantics of contracts on union and intersection type
systems, which have a simple and natural definition from which the other
properties follow. This approach makes sense, and has been continued in future
works, and in particular in~\cite{RootCauseOfBlame}.

@@

Let us recast the problematic example of Figure~\ref{fig:inter-flat-contracts}
in Figure~\ref{fig:inter-flat-contracts-2}). The execution now splits the
intersection into two sub-contracts that are checked separately. If one
component fails, a flag in a global state. In particular, the two threads don't
interact directly, and don't raise blame by themselves, leading this example to run
as expected.
